Spin canonical divisors of log stacky curves

### 2015-06-30 stacky_write_up/spin_cring.tex
join two sparse-looking paragraphs
rem that \Delta can be any effective, label defns

Then a {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$
where $\Delta \in \di X$ is a log divisor and $2\halfcan = K_X +
\Delta + \sum_{i = 1}^{r} \subhalf{e_i} P_i$.

The central object of study in this paper is the {\bf log spin
canonical ring} of $(\sx, \Delta, \halfcan)$ is
\begin{align*}
	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(X, d \halfcan)
\end{align*}

@@

\begin{rem}
\label{rem:separably-rooted}
In fact, the theorem only needs to assume that the stacky curve
is separably rooted, i.e. the residue field at each stacky point
is separable.
\end{rem}

@@

\begin{rem}
\label{rem:explicit-generators}
The proofs of the main theorems in the low genus cases not only
obtain bounds on the degrees of the generators and relations, but
also yield explicit systems of generators and the initial ideal of
relations. Furthermore, our proof of the high genus case also
provides an inductive procedure for determining the generators and
initial ideal of relations for the half-canonical divisor $\halfcan$
 can be written as $\halfcan = \halfcan' + \Lambda$ with $(\halfcan
', \Delta, \sx)$ when $\Lambda \in \di \sx$ effective. In fact,
such a system of generators and relations are known for $\halfcan'$
in many interesting low genus cases, as detailed in Neves
~\cite[Section III.4]{neves:halfcan}.
\end{rem}

@@

\ssec{Stacky Curves and Log Spin Canonical Rings}
\label{ssec:stacky-background}
\todo{combine the below chunk with the near-duplicate section
in the introduction}
A \textbf{stacky curve} $\sx$ over a field $k$ is a smooth proper
geometrically-connected Deligne-Mumford stack of dimension $1$ over
$k$ with a dense open subscheme. A stacky curve is \textbf{tame} if
its stabilizers are coprime to char $k$.

@@

If $P_1, \ldots, P_r$ are the stacky points of a stacky curve $\sx$,
then we use $e_1,\ldots, e_r \in \BZ_{\geq 2}$ to denote the orders
of the stabilizer groups of the points with non-trivial
stabilizers. We call $e_i$ the \textbf{stabilizer order} of $P_i$.
In order to study objects associated with stacky curves, it is often
useful to consider them in the context of ordinary schemes.

\begin{defn}
Let $\sx$ be a stacky curve over $k$ with stacky points $P_1, \ldots,
P_r$ with stabilizer orders $e_1,\ldots, e_r \in \BZ_{\geq 2}$.
Let $X$ be a nonsingular projective (algebraic) curve over $k$ of
genus $g$. Then $X$ is the \textbf{coarse space} associated to $\sx$
if

@@

\begin{defn}
If Weil divisor $D \in \di \sx$ and $D = \sum_{i = 1}^{n} \alpha_i P_i$
with $\alpha_i \in \BQ$, the floor of a divisor $\lfloor D
\rfloor$ is defined to be $\lfloor D \rfloor := \sum_{i = 1}^{n}
\lfloor \alpha_i \rfloor P_i$.
\todo{cite lemma 5.4.7 from VZB maybe?}
\end{defn}

\begin{defn}
Let $\sx$ be a stacky curve with coarse space $X$.
If $D \in \di \sx$ is a Weil divisor, then we define

@@

\begin{defn}
The {\bf log spin canonical ring} of $(\sx, \Delta, \halfcan)$ is
\[
	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, d \halfcan)
\]
\end{defn}

>>>>

Then a {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$
where $\Delta \in \di X$ is a log divisor and $2\halfcan = K_X +
\Delta + \sum_{i = 1}^{r} \subhalf{e_i} P_i$. The central object of
study in this paper is the {\bf log spin canonical ring} of $(\sx,
\Delta, \halfcan)$ is
\begin{align*}
	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(X, d \halfcan)
\end{align*}

@@

\begin{rem}
\label{rem:main-weaker-assumptions}
In fact, the theorem only needs to assume that the stacky curve
is separably rooted, i.e. the residue field at each stacky point
is separable. Furthermore, the proof works even when letting
$\Delta$ be any effective divisor rather than just a log divisor.
\end{rem}

@@

\begin{rem}
\label{rem:explicit-generators}
The proofs of the main theorems in the low genus cases not only
obtain bounds on the degrees of the generators and relations, but
also yield explicit systems of generators and the initial ideal of
relations. Furthermore, our proof of the high genus case also
provides an inductive procedure for determining the generators and
initial ideal of relations for the half-canonical divisor $\halfcan$
can be written as $\halfcan = \halfcan' + \Lambda$ with $(\halfcan',
\Delta, \sx)$ when $\Lambda \in \di \sx$ effective. In fact,
such a system of generators and relations are known for $\halfcan'$
in many interesting low genus cases, as detailed in Neves
~\cite[Section III.4]{neves:halfcan}.
\end{rem}

@@

\ssec{Stacky Curves and Log Spin Canonical Rings}
\label{ssec:stacky-background}
A \textbf{stacky curve} $\sx$ over a field $k$ is a smooth proper
geometrically-connected Deligne-Mumford stack of dimension $1$ over
$k$ with a dense open subscheme. A stacky curve is \textbf{tame} if
its stabilizers are coprime to char $k$.

@@

If $P_1, \ldots, P_r$ are the stacky points of a stacky curve $\sx$,
then we use $e_1, \ldots, e_r \in \BZ_{\geq 2}$ to denote the orders
of the stabilizer groups of the points with non-trivial
stabilizers. We call $e_i$ the \textbf{stabilizer order} of $P_i$.
In order to study objects associated with stacky curves, it is often
useful to consider them in the context of ordinary schemes.

\begin{defn}
\label{defn:coarse-space}
Let $\sx$ be a stacky curve over $k$ with stacky points $P_1, \ldots,
P_r$ with stabilizer orders $e_1,\ldots, e_r \in \BZ_{\geq 2}$.
Let $X$ be a nonsingular projective (algebraic) curve over $k$ of
genus $g$. Then $X$ is the \textbf{coarse space} associated to $\sx$
if

@@

\begin{defn}
\label{defn:divisor-floor}
If Weil divisor $D \in \di \sx$ and $D = \sum_{i = 1}^{n} \alpha_i P_i$
with $\alpha_i \in \BQ$, the floor of a divisor $\lfloor D
\rfloor$ is defined to be $\lfloor D \rfloor := \sum_{i = 1}^{n}
\lfloor \alpha_i \rfloor P_i$.
\todo{cite lemma 5.4.7 from VZB maybe?}
\end{defn}

\begin{defn}
\label{defn:h0-stacky}
Let $\sx$ be a stacky curve with coarse space $X$.
If $D \in \di \sx$ is a Weil divisor, then we define

@@

\begin{defn}
\label{defn:log-spin-canonical-ring}
The {\bf log spin canonical ring} of $(\sx, \Delta, \halfcan)$ is
\[
	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, d \halfcan)
\]
\end{defn}
